Analysis of the included studies

### 2023-05-21 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Adapted the scripts to use use the command line

```{r}
#I/O directories
figs_dir <- "analyses/figs"
data_dir <- "analyses/data"
scripts_dir <- "analyses/scripts"

here::i_am("analyses/scripts/orv_sys_rev_data_analysis.Rmd")
# Create a folder for storing the figures

@@

```{r}
#' re-run the data cleaning step, in case something has changed 
#' TO DO: Use GNU make for this

source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))

# Load the cleaned data 
long_data <- read_rds(here::here(data_dir, "review_data_long_cleaned.rds"))

#The cleaned data without citations
compact_data_init <- read_rds(
  here::here(data_dir, "review_data_compact_cleaned.rds")
  )

# The data with citations 
compact_data_with_citation_keys <- read_rds(
  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'))

>>>>

```{r}
#' if sourced, re-run the data cleaning step, in case something has changed 
#' else if through the terminal, use the arguments passed through the
#' commandline/make
if (is_null(getOption('knitr.in.progress'))) {
source(here::here('./scripts/orv_models_review_data_cleaning.R'))
args <- c(
  here::here("data", "review_data_long_cleaned.rds"),
  here::here("data", "review_data_compact_cleaned.rds"),
  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
  )
} else {
 args <- commandArgs(trailingOnly = TRUE)
}
```

```{r}
# Create a folder for storing the figures

@@

```{r}
# Load the cleaned data 
long_data <- read_rds(args[1])

#The cleaned data without citations
compact_data_init <- read_rds(args[2])

# The data with citations 
compact_data_with_citation_keys <- read_rds(args[3])
